Fourmile Calibrations

### 2023-02-28 calibration_output.Rmd
updates ready for meeting

```{r setup, include=FALSE}
knitr::opts_chunk$set(
  echo = F,
  message = F)

@@

ggplot(gw_maxcumsum, aes(x = flow_type, y = flow_cms, fill = source)) +
  geom_boxplot(position = position_dodge(1)) + 
  ggtitle('Max annual cumulative sums')

ggplot(gw_maxcumsum, aes(x = flow_type, y = flow_cms, fill = source)) +
  geom_boxplot(position = position_dodge(1)) +
  facet_wrap(~flow_type, scales = 'free') +
  ggtitle('Max annual cumulative sums')

@@

tm_shape(hrus_map_tmean) +
  tm_polygons('diff', id = 'value') +
tm_shape(locations_t) +
  tm_symbols(col='blue', size=4)

@@

tm_shape(hrus_map_tmax) +
  tm_polygons('diff', id = 'value') +
tm_shape(locations_t) +
  tm_symbols(col='blue', size=4)

@@

mar_tmax <- tm_shape(hrus_map_tmax_mar) +
  #tm_polygons('mo_tmax_diff', id = 'value') +
  tm_fill('mo_tmax_diff', id = 'value',
          breaks = c(-6,-3,0,3,6)) +
  tm_borders() +
  tm_shape(locations_t) +
  tm_symbols(col='blue', size = 0.25) +
  tm_layout(title = 'March avg tmax',
            legend.outside = T)

@@

apr_tmax <- tm_shape(hrus_map_tmax_apr) +
  tm_fill('mo_tmax_diff', id = 'value',
          breaks = c(-6,-3,0,3,6)) +
  tm_borders() +
  tm_shape(locations_t) +
  tm_symbols(col='blue', size = 0.25) +
  tm_layout(title = 'April avg tmax',
            legend.outside = T)

@@

may_tmax <- tm_shape(hrus_map_tmax_may) +
  tm_fill('mo_tmax_diff', id = 'value',
         breaks = c(-6,-3,0,3,6)) +
  tm_borders() +
tm_shape(locations_t) +
  tm_symbols(col='blue', size = 0.25) +
  tm_layout(title = 'May avg tmax',
            legend.outside = T)

@@

jun_tmax <- tm_shape(hrus_map_tmax_jun) +
  tm_fill('mo_tmax_diff', id = 'value',
          breaks = c(-6,-3,0,3,6)) +
  tm_borders() +
tm_shape(locations_t) +
  tm_symbols(col='blue', size = 0.25) +
  tm_layout(title = 'June avg tmax',
            legend.outside = T)

@@

tm_shape(hrus_map_tmin) +
  tm_polygons('diff', id = 'value') +
tm_shape(locations_t) +
  tm_symbols(col='blue', size=4)

@@

Relative Precip difference

@@

reg_p <- read_csv(here('HRU_output/reg_precipAll.csv'),
                      skip = 21) %>%
  dplyr::select(-starts_with('@')) %>%
  mutate(time = dmy(time)) %>%
  summarize(across(`3`:`19`, ~ mean(.))) %>%
  pivot_longer(cols = `3`:`19`,
               names_to = 'value', 
               values_to = 'precip_avg') %>%
  mutate(value = as.numeric(value))

hrus_map_precip <- left_join(hrus_map_precip, reg_p, by = 'value')

hrus_map_precip <- hrus_map_precip %>%
  mutate(relative_avgcum_diff = precip_avg_cumdiff / precip_avg)

tm_shape(hrus_map_precip) +
  tm_polygons('relative_avgcum_diff', midpoint = NA, palette = 'YlGnBu', id = 'value') +
tm_shape(locations_p) +
  tm_symbols(col='blue', size=4)

@@

## Average soil sat difference comparison

@@

soilavg_grid <- tm_shape(hrus_map_soilsat) +
  tm_polygons('soilsat_all_grid', midpoint = NA, id = 'value') +
  tm_legend(legend.outside = T) +
  tm_layout(main.title = 'Average soil sat')

soilavg_statn <- tm_shape(hrus_map_soilsat) +
  tm_polygons('soilsat_all_statn', midpoint = NA, id = 'value') +
  tm_legend(legend.outside = T)

@@

soilavg_grid_max <- tm_shape(hrus_map_soilsat_max) +
  tm_polygons('avg_max_grid', midpoint = NA, id = 'value') +
  tm_legend(legend.outside = T) +
  tm_layout(main.title = 'Average max soil sat',
            title.position = c('left', 'top'))

soilavg_statn_max <- tm_shape(hrus_map_soilsat_max) +
  tm_polygons('avg_max_statn', midpoint = NA, id = 'value') +
  tm_legend(legend.outside = T)

@@

ETavg_grid <- tm_shape(hrus_map_ET) +
  tm_polygons('ET_all_grid', midpoint = NA, id = 'value') +
  tm_legend(legend.outside = T) +
  tm_layout(main.title = 'Average ET')

ETavg_statn <- tm_shape(hrus_map_ET) +
  tm_polygons('ET_all_statn', midpoint = NA, id = 'value') +
  tm_legend(legend.outside = T)

@@

@@

>>>>

```{r setup, include=FALSE}
knitr::opts_chunk$set(
  echo = F,
  message = F, 
  warning  = F)

@@

ggplot(gw_maxcumsum, aes(x = flow_type, y = flow_cms, fill = source)) +
  geom_boxplot(position = position_dodge(1)) + 
  geom_point(position=position_jitterdodge(),alpha=0.3) +
  ggtitle('Max annual cumulative sums')

ggplot(gw_maxcumsum, aes(x = flow_type, y = flow_cms, fill = source)) +
  geom_boxplot(position = position_dodge(1)) +
  geom_point(position=position_jitterdodge(),alpha=0.3) +
  #geom_point(aes(color = source)) +
  facet_wrap(~flow_type, scales = 'free') +
  ggtitle('Max annual cumulative sums')

### RD and RG by season

```{r flow season, echo = F, fig.width = 12, fig.asp = 0.75, out.width = "100%"}

#group by season and get max sums by season
flow_season <- gw %>%
  dplyr::select(RD1cumsum, RD2cumsum, RG1cumsum, RG2cumsum, date, year, source) %>%
  mutate(month = month(date)) %>%
  mutate(season = case_when(month %in% c(3,4,5,6) ~ 'snowmelt',
                            month %in% c(7,8,9,10) ~ 'monsoon',
                            month %in% c(11,12,1,2) ~ 'baseflow')) %>%
  group_by(source, year, season) %>%
  summarize(yr_season_RD1 = max(RD1cumsum),
            yr_season_RD2 = max(RD2cumsum),
            yr_season_RG1 = max(RG1cumsum),
            yr_season_RG2 = max(RG2cumsum)) %>%
            pivot_longer(!c(year, source, season), names_to = 'flow_type', values_to = 'flow_cms')

flow_season %>%
  ggplot(aes(x = flow_type, y = flow_cms, fill = source)) +
  geom_boxplot(position = position_dodge(1)) +
  geom_point(position=position_jitterdodge(),alpha=0.3) +
  #geom_point(aes(color = source)) +
  facet_wrap(~season, scales = 'free') +
  ggtitle('Max annual season cumulative sums') +
  theme_bw() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
  theme(text = element_text(size = 20))

flow_season %>%
  ggplot(aes(x = flow_type, y = flow_cms, fill = source)) +
  geom_boxplot(position = position_dodge(1)) +
  geom_point(position=position_jitterdodge(),alpha=0.3) +
  #geom_point(aes(color = source)) +
  facet_wrap(~season + flow_type, scales = 'free') +
  ggtitle('Max annual season cumulative sums') +
  theme_bw() +
  theme(text = element_text(size = 20))

@@

tm_shape(hrus_map_tmean) +
  tm_polygons('diff', id = 'value',
              breaks = c(-6,-4,-2,0,2,4,6)) +
tm_shape(locations_t) +
  tm_symbols(col='blue', size=4)

@@

tm_shape(hrus_map_tmax) +
  tm_polygons('diff', id = 'value',
              breaks = c(-6,-4,-2,0,2,4,6)) +
tm_shape(locations_t) +
  tm_symbols(col='blue', size=4)

@@

mar_tmax <- tm_shape(hrus_map_tmax_mar) +
  #tm_polygons('mo_tmax_diff', id = 'value') +
  tm_fill('mo_tmax_diff', id = 'value',
          breaks = c(-6,-4,-2,0,2,4,6)) +
  tm_borders() +
  tm_shape(locations_t) +
  tm_symbols(col='blue', size = 0.25) +
  tm_layout(title = 'March avg tmax',
            legend.outside = T)

@@

apr_tmax <- tm_shape(hrus_map_tmax_apr) +
  tm_fill('mo_tmax_diff', id = 'value',
          breaks = c(-6,-4,-2,0,2,4,6)) +
  tm_borders() +
  tm_shape(locations_t) +
  tm_symbols(col='blue', size = 0.25) +
  tm_layout(title = 'April avg tmax',
            legend.outside = T)

@@

may_tmax <- tm_shape(hrus_map_tmax_may) +
  tm_fill('mo_tmax_diff', id = 'value',
         breaks = c(-6,-4,-2,0,2,4,6)) +
  tm_borders() +
tm_shape(locations_t) +
  tm_symbols(col='blue', size = 0.25) +
  tm_layout(title = 'May avg tmax',
            legend.outside = T)

@@

jun_tmax <- tm_shape(hrus_map_tmax_jun) +
  tm_fill('mo_tmax_diff', id = 'value',
         breaks = c(-6,-4,-2,0,2,4,6)) +
  tm_borders() +
tm_shape(locations_t) +
  tm_symbols(col='blue', size = 0.25) +
  tm_layout(title = 'June avg tmax',
            legend.outside = T)

@@

tm_shape(hrus_map_tmin) +
  tm_polygons('diff', id = 'value',
              breaks = c(-6,-4,-2,0,2,4,6)) +
tm_shape(locations_t) +
  tm_symbols(col='blue', size=4)

@@

@@

# reg_p <- read_csv(here('HRU_output/reg_precipAll.csv'),
#                       skip = 21) %>%
#   dplyr::select(-starts_with('@')) %>%
#   mutate(time = dmy(time)) %>%
#   summarize(across(`3`:`19`, ~ mean(.))) %>%
#   pivot_longer(cols = `3`:`19`,
#                names_to = 'value', 
#                values_to = 'precip_avg') %>%
#   mutate(value = as.numeric(value))
# 
# 
# hrus_map_precip <- left_join(hrus_map_precip, reg_p, by = 'value') 
# 
# hrus_map_precip <- hrus_map_precip %>%
#   mutate(relative_avgcum_diff = precip_avg_cumdiff / precip_avg)
# 
# tm_shape(hrus_map_precip) +
#   tm_polygons('relative_avgcum_diff', midpoint = NA, palette = 'YlGnBu', id = 'value') +
# tm_shape(locations_p) +
#   tm_symbols(col='blue', size=4)

@@

## Average soil sat comparison

@@

soilavg_grid <- tm_shape(hrus_map_soilsat) +
  tm_polygons('soilsat_all_grid', midpoint = NA, id = 'value',
              breaks = c(0.0, 0.05, 0.1, 0.15, 0.2, 0.25, 0.3)) +
  tm_legend(legend.outside = T) +
  tm_layout(main.title = 'Average soil sat')

soilavg_statn <- tm_shape(hrus_map_soilsat) +
  tm_polygons('soilsat_all_statn', midpoint = NA, id = 'value',
              breaks = c(0.0, 0.05, 0.1, 0.15, 0.2, 0.25, 0.3)) +
  tm_legend(legend.outside = T)

@@

soilavg_grid_max <- tm_shape(hrus_map_soilsat_max) +
  tm_polygons('avg_max_grid', midpoint = NA, id = 'value',
              breaks = c(0.1, 0.2, 0.3, 0.4, 0.5, 0.6, 0.7)) +
  tm_legend(legend.outside = T) +
  tm_layout(main.title = 'Average max soil sat',
            title.position = c('left', 'top'))

soilavg_statn_max <- tm_shape(hrus_map_soilsat_max) +
  tm_polygons('avg_max_statn', midpoint = NA, id = 'value',
              breaks = c(0.1, 0.2, 0.3, 0.4, 0.5, 0.6, 0.7)) +
  tm_legend(legend.outside = T)

@@

ETavg_grid <- tm_shape(hrus_map_ET) +
  tm_polygons('ET_all_grid', midpoint = NA, id = 'value',
              breaks = c(0.2, 0.4, 0.6, 0.8, 1.0, 1.2)) +
  tm_legend(legend.outside = T) +
  tm_layout(main.title = 'Average ET')

ETavg_statn <- tm_shape(hrus_map_ET) +
  tm_polygons('ET_all_statn', midpoint = NA, id = 'value',
             breaks = c(0.2, 0.4, 0.6, 0.8, 1.0, 1.2)) +
  tm_legend(legend.outside = T)

@@

## Average ET difference

```{r et diff, echo = F}

ET_hrus <- ET_hrus %>%
  mutate(diff = ET_all_statn - ET_all_grid)

hrus_map_et_diff <- left_join(hrus, ET_hrus, by = 'value')

tm_shape(hrus_map_et_diff) +
  tm_polygons('diff', midpoint = NA, id = 'value')  +
  tm_legend(legend.outside = T) +
  tm_layout(main.title = 'Average ET difference')

@@

## LAI over time

```{r lai over time, echo = F}

# plot time series of LAI over for HRU 1 and HRU 12
hru_grid_select <- hru_grids %>%
  filter(ID == 1 | ID == 12) %>%
  dplyr::select(time, ID, LAI_grid = LAI)

hru_statn_select <- hru_statn %>%
  filter(ID == 1 | ID == 12) %>%
  dplyr::select(time, ID, LAI_statn = LAI)

hru_select <- left_join(hru_grid_select, hru_statn_select, by = c('time', 'ID')) %>%
  rename(value = ID)

# plot time series of LAI over for HRU 1
hru_select %>%
  mutate(year = year(time)) %>% 
  filter(value == 1) %>% 
ggplot(aes(x = time)) +
  geom_line(aes(y = LAI_grid, color = "HRU1_burn_grid"), size = 1) +
  geom_line(aes(y = LAI_statn, color = 'HRU1_burn_statn'), size = 1) +
  ggtitle('LAI over time for HRU 1 (burned)') +
  scale_color_manual(name = 'HRU' , values=c("HRU1_burn_grid"='orange', 
                                            "HRU1_burn_statn"='springgreen4')) +
  theme_bw()

# plot time series of LAI over for HRU 12
hru_select %>%
  mutate(year = year(time)) %>% 
  filter(value == 12) %>% 
ggplot(aes(x = time)) +
  geom_line(aes(y = LAI_grid, color = "HRU12_unburn_grid"), size = 1) +
  geom_line(aes(y = LAI_statn, color = 'HRU12_unburn_statn'), size = 1) +
  ggtitle('LAI over time for HRU 12 (unburned)') +
  scale_color_manual(name = 'HRU' , values=c("HRU12_unburn_grid"='orange', 
                                            "HRU12_unburn_statn"='springgreen4')) +
  theme_bw()
